### 2021-06-18 setup.tex
additional review on Section 3

\kn{Isnt DroidXP a contribution of our approach? If yes, we should start more confidently than saying we "used" it. We should introduce it as a contribution as such.}
We used DroidXP to systematically assess and compare the
performance of test generation tools for mining android sandboxes. DroidXP relies on a
simple \emph{Command Line Interface} (CLI) that simplifies the integration
of different test generation tools and favors the setup and execution 
of the experiments. DroidXP also relies on DroidFax, which instruments
Android apps and collects relevant information about
their execution, including the set of sensitive APIs a given
app calls during a test execution. DroidFax also collects
inter-component communication (ICC) using  static
program analysis.

@@

The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
sandboxes. Since the \blls does not
compute the possible impact of DroidFax into the performance of the test generation tools,
here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.

@@

Similarly to the \blls, besides
method coverage information, our experiments record every call
to \emph{sensitive methods} of the Android
platforms, while a given test case generation tool
is running. We consider the
same set of 97 sensitive methods 
the AppGuard privacy-control framework
uses~\cite{DBLP:conf/esorics/BackesGHMS13}.

Here we take advantage of
DroidXP to execute the different test case generation
tools () in

To answer the first two research questions
(RQ1 and RQ2), we also included in our experiments
a fake test case generation tool named
Joker.

We executed DroidXP using two
configurations. In the first (WOS), we executed DroidXP
using the dataset of 96 pairs of Android apps---each pair
including a benign and a malign version,
the four test case generation tools (DroidBot, DroidMate, Monkey, and Humanoid),
and the \texttt{--disable-static-analysis} option of
DroidFax, which disables the
execution of the DroidFax static analysis
component from the experiment. The WOS configuration
runs the test case generation tools for three times, using
a time limit of three minutes. 
In the second configuration (WS), we executed DroidXP
using the same dataset of 96 pairs of Android apps, though 
executing only a fake test case generator tool (named Joker)
{\bf without} the \texttt{--disable-static-analysis} option.
Joker simulates a test tool that does not
run the Android apps during an experiment execution.

Using the WS configuration, the Execution Phase of
DroidXP does not collect any call to 
sensitive APIs, and thus we can estimate the performance of the
static analysis component of DroidFax (and thus answer
RQ1).
Differently, the WOS configuration
disables the static analysis component of DroidFax and
we could better estimate the true performance of the test
case generation tools for mining android sandboxes 
(answering RQ2).

@@

DroidXP produces a
dataset with the sensitive
APIs that the benign / malign
versions of an app call, during
the execution of each test case
generation tool. We estimate the
performance of a test case generation
tool by considering the percentage of
malwares its \emph{sandbox} is able to
identify.

Recall that we build a sandbox 
during the exploratory of the mining
sandbox approach. This exploratory
phase records the set of 
sensitive APIs a benign version of an
app calls---during the execution of a test
case generation tool. Similarly to the \blls,
we consider that a sandbox of an
app identifies a malware whenever the
malicious version makes a call to a sensitive API  
that has not been recorded during the exploratory
phase.

@@

FlowDroid takes as input an Android Application Package (APK file) and
a set of API methods marked either as {\bf source}
or {\bf sink} (or both). Source methods are those that access \emph{sensitive information} (e.g.,
a method that access the address book), while sink methods are those 
that \emph{might share information with external peers} (e.g., a method that
sends messages to a recipient). We rely on the source-sink definitions
of the FlowDroid implementation~\cite{arzt:pldi-2014,rasthofer-source-sink},
which involves a curate list of source and sink methods (including callbacks and
other Android API methods of interest).
FlowDroid then uses a \emph{context, flow, and field
sensitive analysis} to identify dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.

@@

It is important to note that not all source-sink paths are malign, and then we
follow a specific methodology to identify malwares using taint analysis. That is,
we only report a malware when
FlowDroid finds an additional source-sink path in the malicious version of an app, which
has not been identified when analysing the benign version. To this end, in the third step we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$). If the set S3 is not empty, we assume that FlowDroid
has identified the malware.

>>>>

We designed and implemented DroidXP to systematically assess and compare the
performance of test generation tools for mining android sandboxes. It allows
the integration and comparison of test case generation tools for mining sandboxes, and simplifies
the reproduction of the studies. DroidXP relies on a
simple \emph{Command Line Interface} (CLI) that simplifies the integration
of different test generation tools and favors the setup and execution 
of the experiments. DroidXP also relies on DroidFax, which instruments
Android apps and collects relevant information about
their execution, including the set of sensitive APIs a given
app calls during a test execution. DroidFax also collects
inter-component communication (ICC) using  static
program analysis.

@@

The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
sandboxes~\cite{DBLP:conf/wcre/BaoLL18}. Since the \blls does not
compute the possible impact of DroidFax into the performance of the test generation tools,
here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.

@@

Similarly to the \blls, besides
method coverage information, our experiments record every call
to \emph{sensitive methods} of the Android
platforms, while a given test case generation tool
is running. We consider the
same set of 97 sensitive methods 
from the AppGuard privacy-control framework
uses~\cite{DBLP:conf/esorics/BackesGHMS13}.

We executed DroidXP using two
configurations. In the first (named WOS), we executed DroidXP
using the dataset of 96 pairs of Android apps---each pair
including a benign and a malign version,
the four test case generation tools (DroidBot, DroidMate, Monkey, and Humanoid),
and the \texttt{--disable-static-analysis} option of
DroidFax, which disables the
execution of the DroidFax static analysis
component from the experiment. The WOS configuration
runs the test case generation tools for three times, using
a time limit of three minutes. 
In the second configuration (named WS), we executed DroidXP
using the same dataset of 96 pairs of Android apps, though 
executing only a fake test case generator tool (named Joker)
{\bf without} the \texttt{--disable-static-analysis} option.
Joker simulates a test tool that does not
run the Android apps during an experiment execution.

Using the WS configuration, the Execution Phase of
DroidXP does not collect any call to 
sensitive APIs, and thus we can estimate the performance of the
static analysis component of DroidFax (answering
RQ1).
Differently, the WOS configuration
disables the static analysis component of DroidFax and
we could better estimate the true performance of the test
case generation tools for mining android sandboxes 
(answering RQ2). For comparison purpose, we also
executed the four test case generation tools using the
DroidFax static analysis component.

@@

DroidXP produces a
dataset with the sensitive
APIs that the benign / malign
versions of an app call, during
the execution of each test case
generation tool. We estimate the
performance of a test case generation
tool by considering the percentage of
malwares in our dataset
its resulting sandbox is able to identify .

Recall that we build a sandbox 
during the exploratory phase of the mining
sandbox approach. This exploratory
phase records the set of 
sensitive APIs a benign version of an
app calls---during the execution of a test
case generation tool. Similarly to the \blls,
we consider that a sandbox of an
app identifies a malware whenever the
malicious version makes a call to a sensitive API  
that has not been recorded during the exploratory
phase (see Figure~\ref{fig:settings1}).

\begin{figure}
  \centering{\includegraphics[scale=0.4]{images/first-study-settings.pdf}}
  \caption{Overview of our approach for malware identification in the first study.}
  \label{fig:settings1}
\end{figure}

@@

FlowDroid takes as input an Android Application Package (APK file) and
a set of API methods marked either as {\bf source}
or {\bf sink} (or both). Source methods are those that access \emph{sensitive information} (e.g.,
a method that access the user location), while sink methods are those 
that \emph{might share information with external peers} (e.g., a method that
sends messages to a recipient). We rely on the source-sink definitions
of the FlowDroid implementation~\cite{arzt:pldi-2014,rasthofer-source-sink},
which involves a curate list of source and sink methods (including callbacks and
other Android API methods of interest).
FlowDroid then uses a \emph{context, flow, and field
sensitive analysis} to identify dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.

@@

It is important to note that not all source-sink paths are malign, and then we
follow a specific methodology to identify malwares using taint analysis. That is,
we only report a malware when
FlowDroid finds an additional source-sink path in the malicious version of an app, which
has not been identified when analysing the benign version. Therefore, in the third step we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$). If the set S3 is not empty, we assume that FlowDroid
has identified the malware.
